Constraints on the masses of substructures in $x$ lens galaxies

### 2016-11-18 doc/Paper2/ms.tex
self cite

@@

This work was funded by a Marsden Fast Start grant from the Royal Society of
New Zealand.

>>>>

\citet{lensing2} presented a model of the prior information used to perform
inference from an image of a lensed galaxy. In this paper, we used a slightly
modified model.

@@

This work was supported by a Marsden Fast Start grant from the Royal Society of
New Zealand. We also made use of resources provided by the Centre for
eResearch at the University of Auckland.
